%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Brandon Thompson} % Your name
\address{725 Hyde Parke Blvd.\ \\ Lakeland, Florida 33805} % Your secondary address (optional)
\address{4700 Research Way \\ Lakeland, Florida 33805} % Your address
\address{(386) 466-6700 \\ bthompson5517@floridapoly.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Florida Polytechnic University, Florida} \hfill {\em August 2017 - May 2021} 
\\ Bachelor of Science Computer Science\hfill {Current GPA: 3.61}
\\ Concentration: Cybersecurity
%\\{\bf } \hfill {\em July 2013 - June 2017} 
%\\ Bachelor of Engineering, Civil.\hfill { Overall Percentage: 68.14 }
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
\end{rSection}

\begin{rSection}{Career Objective}
 To work for an organization which provides the opportunity to improve my skills and knowledge
 to grow along with the organization's objectives.
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & Java, C++, C, Python, CLIPS, PHP\\
%Modeling and Analysis \ & AutoCad, SolidWorks \\
%Soldering \ & Through-hole, PCB, Wire-to-wire\\
Software \& Tools & MS Office, Latex, Windows OS, Linux OS\\

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Haines City Technology Management Department}{February 2020 - July 2020}{Intern}{}
	\item Inventory management with Excel. 
	\item Basic desktop and printer support. Replacing and cleaning hardware components.
	\item Hardware installation of servers and other network devices, desktops and cameras.
	\item Writing of Standard Operating Procedure and Cost-Based Analysis documents.
	\item Large area of service for the entire Haines City infrastructure including fire department, police department, road maintenance, city hall and community centers.
	\item Creation of Windows 7 Kiosk machines through registry edits with emphasis on securing the system from malicious users.
	\item Nagios monitoring software setup and installation.
	\item Creation of a inventory database with Microsoft Access.
\end{rSubsection}

\begin{rSubsection}{Florida Polytechnic University}{May 2018 - Summer 2019}{Research Assistant}{}
	\item Co-authored multiple research papers under the lead of Dr.\ Robert Steele.\\
	Machine learning-based prediction of prolonged length of stay in newborns. 2018\\
	Data mining for generalizable pre-admission prediction of elective length of stay. 2019
	\item Speaker at the IEEE Computing and Communication Workshop and Conference.
	\item Applied machine-learning algorithms through Weka software for prediction of prolonged length of stay of hospital patients.
\end{rSubsection}

\end{rSection}

\newpage
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Academic Achievements} 
% Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
%\item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
%\end{rSection}

%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Relevant Coursework}
	\begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }
		
		% Legal Ethical and Management Issues in Technology \ & {\em IDS 2144}\\
		% Machine Learning \ & {\em CAP 4612}\\
		% Profession Experience Internship & {\em IDS 4941}\\
		% Computer Security \ & {\em CIS 4367}\\
		% Introduction to Computer Networks \ & {\em CNT 3004}\\
		% Mobile Device Applications \ & {\em COP 4656}\\
		Operating System Concepts \ & {\em COP 4610}\\
		Computer Architecture and Organization \ & {\em EEL 4768}\\
		% Applied Cryptography \ & {\em CIS 4362}\\
		Software Security Testing \ & {\em CEN 4088}\\
		% Artificial Intelligence \ & {\em CAP 4630}\\
		Software Engineering \ & {\em CEN 4010}\\
		% Digital Media Production \ & {\em DIG 2520}\\
		Algorithm Design and Analysis\ & {\em COP 4531}\\
		% Data Structures \ & {\em COP 4415}\\
		% Database 1 \ & {\em COP 3710}\\
		% Digital Logic Design \ & {\em EEL 3702}\\
		Computer Programming 2 \ & {\em COP 3330}\\
		Computer Programming 1 \ & {\em COP 2272}\\
		% Introduction to Unix \ & {\em COP 3353}\\
		% Statistics 1 \ & {\em STA 2023}\\
		% Discrete Mathematics \ & {\em MAD 2104}\\
		% Computational Linear Algebra \ & {\em MAS 3114}\\
		% Differential Equations \ & {\em MAP 2302}\\
		% Physics 2 \ & {\em PHY 2049/L}\\
		% Introduction to Computation and Programming \ & {\em COP 2271}\\
		% Concepts and Methods \ & {\em EGN 1007}\\
		% Technical Writing \ & {\em ENC 2210}\\
		% Analytic Geometry and Calculus 2 \ & {\em MAC 2312}\\
		% Physics 1 \ & {\em PHY 2048/L}\\
		% Biology 1 \ & {\em BSC 1010}\\
		% English Comp. 1 \ & {\em ENC 1101}\\
		% Introduction to Stem {\em IDS 1380}\\
		% Analytic Geometry and Calculus 1 {\em MAC 2311}\\
		% First Year Experience \ & {\em SLS 1106}\\
	\end{tabular}
\\
\end{rSection}

\begin{rSection}{School Projects} \itemsep -3pt
	\item Senior Design - Computer Vision model for Whitning-Turner Construction company to track various metrics on sites such as the arrival time of supplies.
	\item Operating Systems Concepts - Implementing system calls and Multilevel Feedback Queue Scheduler on basic operating system.
	\item Mobile Device Applications - Ingredient tracking app that allows the user to search database for recipes that contain specific ingredients.
	\item Software Engineering - Hotel Management System that allows guest and employee logins. Guests can reserve rooms or request service and employees can track service requests.
	\item Database 1 - Creation of SQL database that tracks nutritional data for the on campus cafeteria.
\end{rSection}

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular} \itemsep -3pt
	\item Have seven consecutive years as member of a robotics team. (2013 - Present)\\
	Four years as part of FIRST FRC Robotics team 3556. (2013-2017)\\
	Presently a member of VEX-University.
	\item Learning full-stack development in my free time.
	\item Volunteered for two weeks at a SeriousFun Children's Network summer camp for kids with serious illnesses. (Summer 2019)
\end{rSection}

\begin{rSection}{Personality Traits}
	\item Highly motivated and eager to learn new things.
	\item Very honest and modest person, I do not like to show off or gloat.
	\item Ability to work as an individual as well as in groups.
	\item Diligent and organized, being organized facilitates my workflow and helps me accomplish tasks on time.
\end{rSection}
\end{document}
