%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Brandon Thompson} % Your name
\address{725 Hyde Parke Blvd \\ Lakeland, Florida 33805} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
\address{(386) 466-6700 \\ bthompson5517@floridapoly.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{}
\ \\\
\\
\today \\
FireEye\\
Denver, Colorado\\


Dear Hiring Manager: \\

My name is Brandon Thompson and I am writing to express my interest in the entry level Associate Security Consultant position at FireEye.
I am excited for the opportunity to work for FireEye because cybersecurity is a passion of mine and FireEye is one of the top cybersecurity firms.
This position aligns perfectly with my goal of becoming a Security Consultant or penetration tester and developing my skills in the industry.

Currently, I am attending Florida Polytechnic University and will graduate in the Spring of 2021 with a Bachelor's of Science in Computer Science with a concentration in cybersecurity.
Throughout my college career, I have taken classes such as Computer Security, Software Security Testing, Introduction to Computer Networks, Applied Cryptography, and multiple programming classes that have taught me a lot about security concepts how to apply them.

What attracted me most to FireEye was the contributions to high-profile security breaches like Target and Sony Pictures, that we have researched in class.
I look forward to meeting you to further discuss my qualifications and how I will be an asset to FireEye.
Thank you for your time and consideration.


Sincerely,

Brandon Thompson


\end{rSection}
\end{document}
