\subsection{Chapter 1}
\subsubsection{Terms and Evolution of Hacking}
\textbf{Hackers / Crackers}
\begin{itemize}
    \item Access to computer system or network without authorization.
    \begin{itemize}
        \item Breaks the law; can go to prison.
    \end{itemize}
\end{itemize}

\textbf{Ethical Hacker}
\begin{itemize}
    \item Performs most of the same activities as a hacker with the owners / company's permission.
\end{itemize}

Hackers became more prolific and dangerous after the availability of the Internet expanded to include the general public.
Originally hacking was the skillful modification of systems.
As the Internet began to include more people and technology, there was more of a following for hacking.
First for fun or curiosity, then for maliciousness and financial reasons.

\subsubsection{What is Hacking}
\begin{itemize}
    \item Stealing passwords and usernames - ''Theft of access'' 
    \item Network intrusions - Form of digital trespassing
    \item Social Engineering - Humans are the weakest point of a computer system.
    \item Posting / transmitting illegal material - Illegal material can spread very quickly with the use of social media.
    \item Financial Fraud - Deception of one party to elicit information or system access typically for financial gain to to cause damage.
    \item Software / data piracy - the possession, duplication / distribution of software in violation of license agreement / act of removing copy protection.
    \item Dumpster Diving - gathering of material that has been discarded or left in unsecured or unguarded receptacles.
    \item Creating and Planting Malicious Code - refers to items such as viruses, worms, spyware, adware, rootkits, and other types of malware. (any type of software written to wreak havoc, destruction or disruption.)
    \item Unauthorized Destruction or Alteration - Modifying, destroying, or tampering of information without permission.
    \item Data diddling - Unauthorized modification of information to cover up other malicious activity.
    \item Denial of Service (DoS/DDoS) - Overload a systems resources so it cannot provide the required services to its users.
    \item Ransomware - encryption of key files on a system for the purpose of extracting payment from the victim.
\end{itemize}

\subsubsection{Types of Hackers}
\begin{itemize}
    \item Black-Hat Hackers: Bad guys, may or may not have an agenda (Criminal)
    \item White-Hat Hackers: Good guys, have a code of ethics.
    \item Gray-Hat Hackers: Could be good or bad (do not trust)
    \item Suicide Hackers: Trying to prove a point, are not stealthy because they do not care about repercussions.
    \item Script Kiddies: No or limited training, use prebuilt tools, mainly curious.
\end{itemize}

\subsubsection{Motives of Hackers}
\begin{itemize}
    \item Monetary - financial gain
    \item Status - Increased reputation within their communities
    \item Terrorism - To scare, intimidate, or cause panic to the target group or the victims
    \item Revenge / Hatred - Disgruntled employees
    \item Hacktivism - Bring attention to a cause, group, or political ideology.
    \item Fun - Attacks with no specific goal
\end{itemize}


