\documentclass[12pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
%\usepackage[margin=1in]{geometry}
\usepackage[onehalfspacing]{setspace}
%\usepackage[doublespacing]{setspace}
%\usepackage{amsmath, amssymb, amsthm}
\usepackage{enumerate, enumitem}
%\usepackage{fancyhdr, graphicx, proof, comment, multicol}
\usepackage[none]{hyphenat} % This command prevents hyphenation of words
%\binoppenalty=\maxdimen % This command and the next prevent in-line equation breaks
%\relpenalty=\maxdimen

\usepackage{hyperref}

%    Good website with common symbols
% http://www.artofproblemsolving.com/wiki/index.php/LaTeX%3ASymbols
%    How to change enumeration using enumitem package
% http://tex.stackexchange.com/questions/129951/enumerate-tag-using-the-alphabet-instead-of-numbers
%    Quick post on headers
% http://timmurphy.org/2010/08/07/headers-and-footers-in-latex-using-fancyhdr/
%    Info on alignat
% http://tex.stackexchange.com/questions/229799/align-words-next-to-the-numbering
% http://tex.stackexchange.com/questions/43102/how-to-subtract-two-equations
%    Text align left-center-right
% http://tex.stackexchange.com/questions/55472/how-to-make-text-aligned-left-center-right-in-the-same-line

%\usepackage{microtype} % Modifies spacing between letters and words
%\linespread{1.1} 

\usepackage[
backend=biber,
style=mla
]{biblatex}
\addbibresource{informative_essay.bib}

\begin{document}
% This is the Header
% Make sure you update this information!!!!
\noindent
\textbf{IDS 2144.01} \hfill \textbf{Brandon Thompson} \\
\normalsize Prof. LeFrancois \hfill Due Date: 6/1/2020 \\

% This is where you name your homework
\begin{center}
\textbf{Informative Essay}
\end{center}

	Between 2004 and 2009 almost 40,000 mass layoffs occurred in the US, affecting over
	7 million workers. \autocite{sucher} Technology is advancing at a rapid rate, with
	advancements in Artificial Intelligence (AI) and robotics, your job could soon be
	automated. This paper will cover the ethical implications of replacing large amounts
	of workers with robotic systems. There are many issues with replacing workers with
	machines. What are the economic impacts of laying off hundreds of workers. Should 
	employers be allowed to replace capable workers with machines? What should be done
	with the workers who have been replaced? I used to be an intern for a factory that
	assembled lithium-ion battery packs for medical and military level equipment. Every
	year that I was interning there there was another machine that was faster and could
	do more than the last year. While i was at the factory, they were in the process of
	expanding their operation so they did not need to lay anybody off, but I got to
	witness firsthand how automation has changed the manufacturing process.
	
	Automation of a job is not the same as the automation of a task Bessen states in his
	paper that a group of researchers  evaluated 70 occupations and deemed 37 of them
	''fully automatable,'' and predicted that in the future, half of all jobs are
	susceptible to complete automation. However, none of the 37 jobs listed have been
	completely automated so far. \autocite{bessen}

	Automating jobs could be a good thing for the workers, people in the welding profession
	can develop eye, nose and throat irritation as well as pulmonary infections, heart
	disease, and lung and throat cancer as a product of working with hazardous materials.
	\autocite{pham} Replacing these workers with a machine would not only increase production
	for the company, it will reduce health issues caused by welding.



	\newpage
	\printbibliography
\end{document}
